Psychological Needs During Intergroup Contact: Three Experience Sampling Studies

### 2022-11-08 Methods-and-Results.Rmd
Update Methods-and-Results.Rmd
tbl and fgr refs

NEEDS TO GO SOMEWHERE: To build further confidence in our results, we assessed two additional models that might offer alternative explanations. First, to ensure that the effect of core need fulfillment is specific to an actual contact, we compared the effect to core need fulfillment in situations without an intergroup contact.

@@

The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A. Correlations and descriptive statistics of the included variables are available in Table \ref{tab:descrFullWide} and Table \ref{tab:descrOutWide}.

@@

For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”. Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50). The self-determination theory need measurements are described in Appendix \ref{app:AppendixRobustness}.

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis in two steps. First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`). However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`). And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see Table \ref{tab:intergroupGeneralTblLong}).  -->
We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently). Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors. Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate that the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}. 
Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data. While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality. We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.

\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need. This should, in turn, be due to a higher perceived contact quality. We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}).

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis as in Study 1. We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see Table \ref{tab:intergroupGeneralTblLong} and Figure \ref{fig:ContactHypothesis}).  -->
We tested the most general contact hypothesis as we did for Study 1. We, again, used a multilevel regression analysis to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently). We again added the participant means back into the model. Because these are the means of the contact dummy variables they are the proportion of measurements that included a particular contact. This not only adjusts the model for unequal cell sizes but allows us to see whether between subject differences in the relative number of interactions had an effect on outgroup attitudes. We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`). The relative number of non-outgroup interactions showed no such effect (for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, as well as Online Supplementary Material A). 
Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.

@@

We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is subsumed by the perceived interaction quality if considered jointly. We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`). Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment} for full results). These results are consistent with the results in Study 1. We, thus, find support for our hypotheses that the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.

@@

The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A. Correlations and descriptive statistics of the included variables are available in Tables \ref{tab:descrFullWide} and \ref{tab:descrOutWide}.

@@

\subsubsection{Contact Hypothesis}
<!-- As in Studies 1 and 2, we first conducted a general contact hypothesis test. We found no correlation between the overall number of intergroup contacts and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (|\textit{r}| < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we did find a significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). When considering the number of interactions and average interaction quality jointly in a linear regression, we only found a main effect of average perceived interaction quality on outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect. This result mirrors that of Study 1 but is inconsistent with the second study.  -->
Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see Table \ref{tab:intergroupGeneralTblLong}, Figure \ref{fig:ContactHypothesis}, and Online Supplementary Material A). Thus, in our third data set we found within person contemporaneous effect of intergroup contact was consistent across all three studies.

@@

Similarly to the previous studies, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly. We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`). Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}). These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.

@@

As we did with core need fulfillment, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly. In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`). Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see Table \ref{tab:intergroupNeedsTblLong} and Figure \ref{fig:AllportNeedFulfillment}). These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.

@@

\begin{center}
    \noindent\rule{8cm}{0.4pt}\\
    \hl{\textit{New Section:}}\\
    \vspace{-0.25cm}
    \noindent\rule{8cm}{0.4pt}
\end{center}

>>>>

@@

The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A. Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.

@@

For the core situational need, we asked participants in an open ended text field: “\textit{What was your most important goal [during the interaction / this morning / this afternoon]?}”. Then, with reference to the text entry, we asked how much this core need was fulfilled during the interaction or the past daytime period: “\textit{[The interaction / You] fulfilled your goal: [-previous text entry-]}” on a continuous slider scale ranging from strongly disagree (-50) to strongly agree (+50). The self-determination theory need measurements are described in \appref{app:AppendixRobustness}.

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis in two steps. First, we assessed whether overall between participants more intergroup interactions were related to to more positive average outgroup attitudes. Second, we tested whether a potential positive effect on outgroup attitudes depended on the interaction quality (jointly with the number of interactions). We find that neither the overall number of contacts nor the number of experience sampling responses with a contact were significantly related with the average outgroup attitudes (all | \textit{r} | < `r rContactAvgMax`, all \textit{p} > `r pContactAvgMin`). However, we did find a medium sized correlation between the participants' average contact quality and their average outgroup attitudes (\textit{r} = `r format(round(rAttitudeQuality$r[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],2), nsmall = 2)`, \textit{p} = `r format(round(rAttitudeQuality$P[rownames(rAttitudeQuality$r) != "AvAttitude","AvAttitude"],3), nsmall = 3)`). And when considering the number of contacts and average contact quality jointly in a linear regression, we additionally found a statistically significant interaction term (\textit{b} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlWorker$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlWorker$lmAttFreqQualX))["SumContactNL_c:AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlWorker$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c:AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`), where in our sample with an increasing number of contacts the positive effect of average contact quality becomes weaker (also see \tblref{tab:intergroupGeneralTblLong}).  -->
We used a multilevel regression to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup contact is indeed associated with significantly more positive outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlWorker$lmeInterceptAttType, lmerCI = mdlWorker$lmerInterceptAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently). Additionally, while multi-level regressions are generally robust against unequal cell sizes, we correct for inequalities by use centered predictors and reintroducing the means as level two predictors. Nonetheless, we also offer an analysis of the joint data sets in Online Supplemental Material A (for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A)\footnote{Interestingly, adding random slopes to this model did not explain additional variance. This is unusual and might indicate that the effect is very consistent across participants. However, the small number of participants, or other measurement issues provide an alternative explanation, which is why we offer a combined data set analyses following the individual studies.}. 
Thus, in our first data we find initial evidence that outgroup contacts show a positive effect on outgroup attitudes within real-life data. While this offers support for the most basic premise of the intergroup contact hypothesis (i.e., that any interaction will lead to more positive outgroup attitudes), this analysis does not consider any notion of interaction quality. We assess the conditional effects of interaction numbers and interaction quality ratings after we report on the individual studies to avoid under-powered analyses.

\subsubsection{Core Need}The main proposal of our article is that the success of an outgroup contact might be explained by whether or not the contact fulfilled the person's core situational need. This should, in turn, be due to a higher perceived contact quality. We sequentially test whether the fulfillment of the core need during an interaction is (1) related to more positive outgroup attitudes, (2) higher perceived contact quality, and (3) whether the variance explained by the core need is subsumed by the perceived contact quality if considered jointly (for full regression results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}).

@@

\subsubsection{Contact Hypothesis}
<!-- We tested the most general contact hypothesis as in Study 1. We found a significant correlation with average outgroup attitudes for both the total number of outgroup interactions (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNLAll, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`) and the number of measurement beeps with an interaction (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$SumContactNL, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we found no significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtStudentSupp$studentContactFreq$AvQuality, dtStudentSupp$studentContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). Thus, when considering the number of interactions and average interaction quality jointly in a linear regression, we find a main effect of intergroup contacts to predict outgroup attitudes (\textit{b} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlStudent$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlStudent$lmAttFreqQualX))["SumContactNL_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlStudent$lmAttFreqQualXEta %>% filter(Parameter == "SumContactNL_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of average perceived contact quality and no significant interaction term (for full results see \tblref{tab:intergroupGeneralTblLong} and \fgrref{fig:ContactHypothesis}).  -->
We tested the most general contact hypothesis as we did for Study 1. We, again, used a multilevel regression analysis to check whether having an interaction with an outgroup member had a situational (i.e., contemporaneous) effect within the participants. We find that having an outgroup interaction is indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch person (which did not relate to outgroup attitudes independently). We again added the participant means back into the model. Because these are the means of the contact dummy variables they are the proportion of measurements that included a particular contact. This not only adjusts the model for unequal cell sizes but allows us to see whether between subject differences in the relative number of interactions had an effect on outgroup attitudes. We find that in this data set participant-level outgroup contact proportions were also a positive predictor of outgroup attitudes (`r MlCoeffLatex(lmeMdl = mdlStudent$lmeSlopesAttType, lmerCI = mdlStudent$lmerSlopesAttTypeCI, varName = "OutgroupInteractionM")`). The relative number of non-outgroup interactions showed no such effect (for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, as well as Online Supplementary Material A). 
Thus, in our second data set we find that outgroup contacts show a positive effect on outgroup attitudes in the moment and on average between participants.

@@

We again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is subsumed by the perceived interaction quality if considered jointly. We find that in the multilevel models, the fulfillment of core situational needs during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCore, lmerCI = mdlStudentOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Qlt$lmeSlopesCore, lmerCI = mdlStudentOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFullfillment_cwc")`). Additionally, if we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that virtually all variance is explained by perceived interaction quality (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "quality_overall_cwc")`) and only little unique variance is still explained by core need fulfillment (`r MlCoeffLatex(lmeMdl = mdlStudentOut$Att$lmeSlopesCoreQlt, lmerCI = mdlStudentOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFullfillment_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment} for full results). These results are consistent with the results in Study 1. We, thus, find support for our hypotheses that the fulfillment of core situational needs had a significant influence on outgroup attitudes and that this effect is likely explained by its effect through perceived interaction quality.

@@

The full surveys are available in our OSF repository \citep{KreienkampMasked2022a} and the full data description is available in Online Supplementary Material A. Correlations and descriptive statistics of the included variables are available in \tblref{tab:descrFullWide} and \tblref{tab:descrOutWide}.

@@

\subsubsection{Contact Hypothesis}
<!-- As in Studies 1 and 2, we first conducted a general contact hypothesis test. We found no correlation between the overall number of intergroup contacts and average outgroup attitudes --- for neither the total number of outgroup interactions nor the number of measurement beeps with an interaction (|\textit{r}| < `r cor(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} > `r cor.test(dtMedicalSupp$medicalContactFreq$SumContactNL, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). However, we did find a significant correlation between the participants' average interaction quality and their average outgroup attitudes (\textit{r} = `r cor(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude) %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r cor.test(dtMedicalSupp$medicalContactFreq$AvQuality, dtMedicalSupp$medicalContactFreq$AvAttitude)$p.value %>% round(3) %>% format(nsmall=3)`). When considering the number of interactions and average interaction quality jointly in a linear regression, we only found a main effect of average perceived interaction quality on outgroup attitudes (\textit{b} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Estimate"] %>% round(2) %>% format(nsmall=2)`, \textit{t}(`r mdlMedical$lmAttFreqQualX$df.residual`) = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","t value"] %>% round(2) %>% format(nsmall=2)`, \textit{p} = `r coef(summary(mdlMedical$lmAttFreqQualX))["AvQuality_c","Pr(>|t|)"] %>% round(3) %>% format(nsmall=3)`, $\eta_p^2$ = `r mdlMedical$lmAttFreqQualXEta %>% filter(Parameter == "AvQuality_c") %>% select(Eta2_partial) %>% as.numeric %>% round(2) %>% format(nsmall=2)`) but no significant effect of the number of contacts nor an interaction effect. This result mirrors that of Study 1 but is inconsistent with the second study.  -->
Additionally, in a multilevel regression to check for contemporaneous within person effects, we found that having an outgroup interaction was indeed associated with significantly more positive outgroup attitudes within the participants (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedical$lmeSlopesAttType, lmerCI = mdlMedical$lmerSlopesAttTypeCI, varName = "OutgroupInteractionC")`), even after controlling for having an interaction with a non-Dutch (which did not relate to outgroup attitudes independently; for full results see \tblref{tab:intergroupGeneralTblLong}, \fgrref{fig:ContactHypothesis}, and Online Supplementary Material A). Thus, in our third data set we found within person contemporaneous effect of intergroup contact was consistent across all three studies.

@@

Similarly to the previous studies, we again sequentially tested whether the fulfillment of the core need during an interaction was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by the core need is assumed by the perceived interaction quality if considered jointly. We find that the fulfillment of the core need during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCore, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesCore, lmerCI = mdlMedicalOut$Qlt$lmerSlopesCoreCI, varName = "KeyNeedFulfillment_cwc")`). Additionally, once we consider the influences of core need fulfillment and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by core need fulfillment was roughly half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesCoreQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesCoreQltCI, varName = "KeyNeedFulfillment_cwc")`; for full results see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}). These results indicate that in this data set outgroup attitudes were significantly predicted by the fulfillment of core situational needs and this effect partially emerged via its effect on perceived interaction quality.

@@

As we did with core need fulfillment, we sequentially tested whether the fulfillment of Allport's contact conditions was (1) related to more positive outgroup attitudes, (2) higher perceived interaction quality, and (3) whether the variance explained by Allport's Conditions is assumed by the perceived interaction quality if considered jointly. In the multilevel models we find that the fulfillment of Allport's Conditions during outgroup contacts was associated with more positive outgroup attitudes (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllport, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`) and also predicted higher perceived interaction quality (random slopes model; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Qlt$lmeSlopesAllport, lmerCI = mdlMedicalOut$Qlt$lmerSlopesAllportCI, varName = "AllportsCondition_cwc")`). Moreover, when we consider the influences of Allport's Conditions and interaction quality on outgroup attitudes jointly, we find that perceived interaction quality is a substantially stronger predictor (random slopes mode; `r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "qualityOverall_cwc")`) and the unique variance explained by Allport's Conditions was less than half of its original effect size (`r MlCoeffLatex(lmeMdl = mdlMedicalOut$Att$lmeSlopesAllportQlt, lmerCI = mdlMedicalOut$Att$lmerSlopesAllportQltCI, varName = "AllportsCondition_cwc")`; also see \tblref{tab:intergroupNeedsTblLong} and \fgrref{fig:AllportNeedFulfillment}). These results indicate that in this data set the fulfillment of Allport's conditions had a significant influence on outgroup attitudes and this effect is likely, in parts, explained by its effect through perceived interaction quality.

@@
